---
title: "Assessment 1"
author: "Joanne Elizalde-Hernandez"
date: "16/08/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


library(tidyverse)
library(ggplot2)
library(dplyr)
library(skimr)
library(janitor)
```

# RMarkdown ***editing***

R is a terrific tool for telling stories with graphics and data, but sometimes you need words too. R Markdown weaves together narrative text and code to produce elegantly formatted reports, papers, books, slides and more.

R Markdown documents are fully reproducible. Use a productive notebook interface to weave together narrative text and code to produce elegantly formatted output. Use multiple languages including R, Python, and SQL.

R Markdown supports dozens of static and dynamic output formats including HTML, PDF, MS Word, Beamer, HTML5 slides, Tufte-style handouts, books, dashboards, shiny applications, scientific articles, websites, and more.

[Markdown Basics](https://rmarkdown.rstudio.com/lesson-8.htm) are available from the R Markdown studio website.


```{r}
read.csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv")


```

