---
title: "Assessment 1"
author: "Joanne Elizalde-Hernandez"
date: "16/08/2021"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#install.packages(scales)
#install.packages(lubridate)


library(tidyverse)
library(ggplot2)
library(dplyr)
library(skimr)
library(janitor)
theme_set(theme_light())
```

# RMarkdown ***editing***

**R** is a terrific tool for telling stories with graphics and data, but sometimes you need words too. **R Markdown** *weaves together* narrative text and code to produce elegantly formatted reports, papers, books, slides and more.

R Markdown documents are fully reproducible. Use a productive notebook interface to weave together narrative text and code to produce elegantly formatted output. Use multiple languages including R, Python, and SQL.

R Markdown supports dozens of static and dynamic output formats including HTML, PDF, MS Word, Beamer, HTML5 slides, Tufte-style handouts, books, dashboards, shiny applications, scientific articles, websites, and more.

* [Markdown Basics](https://rmarkdown.rstudio.com/lesson-8.htm) are available from the ***R Markdown studio*** website.


```{r}
download.file(url = "https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv",
 destfile = "fastfood.csv")

fastfood<- read.csv("fastfood.csv",
              stringsAsFactors = FALSE)

data <- fastfood

fastfood <-read.csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv")

head(fastfood)
head(fastfood, n = 10)

knitr::kable(head(fastfood[, 1:5]), "simple")


fastfood%>%
  filter(calories>1000)


dont_eat_this<-data.frame(
fastfood%>%
    filter(total_fat>40 & total_carb>80))


data%>%
  filter(restaurant== "Mcdonalds")
 

```

## Part 2


```{r}
library(skimr)

str(fastfood)

fastfood %>% count(restaurant)

fastfood %>%
  group_by(restaurant) %>%
  summarise(calories= mean(calories))


average_calories <- data.frame(fastfood %>%
  group_by(restaurant) %>%
  summarise(calories= mean(calories)))


#graph with colour
fastfood %>%
  ggplot(aes(total_fat, restaurant, fill = restaurant)) +
    geom_col()+
  coord_flip()

 
```

**Column charts** are useful for showing data changes over a period of time or *for illustrating comparisons among items*. In **column charts**, categories are typically organized along the horizontal axis and values along the vertical axis.

Like bar charts, **column charts** can be used to plot both nominal data and ordinal data, and they can be used instead of a pie chart to plot data with a part-to-whole relationship.

```{r}
max_total_fat <- data.frame(fastfood) %>%
  group_by(restaurant) %>%
  summarise(total_fat= max(total_fat))

```

