---
title: "Assessment 1"
author: "Joanne Elizalde-Hernandez"
date: "16/08/2021"
output: html_document
---


```{r setup, include=FALSE}
#install.packages("tidyverse")
#install.packages("skimr")
#install.packages("ggplot2")

library(tidyverse)
library(ggplot2)
library(skimr)
theme_set(theme_light())
```

# RMarkdown ***editing***

**R** is a terrific tool for telling stories with graphics and data, but sometimes you need words too. **R Markdown** *weaves together* narrative text and code to produce elegantly formatted reports, papers, books, slides and more.

R Markdown documents are fully reproducible. Use a productive notebook interface to weave together narrative text and code to produce elegantly formatted output. Use multiple languages including R, Python, and SQL.

R Markdown supports dozens of static and dynamic output formats including HTML, PDF, MS Word, Beamer, HTML5 slides, Tufte-style handouts, books, dashboards, shiny applications, scientific articles, websites, and more.

* [Markdown Basics](https://rmarkdown.rstudio.com/lesson-8.htm) are available from the ***R Markdown studio*** website.

```{r}
download.file(url = "https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv",
 destfile = "fastfood.csv")

fastfood<- read.csv("fastfood.csv",
              stringsAsFactors = FALSE)

#6.name of the variable .
data <- fastfood

#7.Display the first 10 rows of the dataset.
head(fastfood, n = 10)

#first 10 rows of the dataset and the first 5 variables .
knitr::kable(fastfood[1:10, 1:5])

#8.observations that has more than 1000 calories.
fastfood%>%
  filter(calories>1000)

#9.Observations with more than 40 in total_fat and more than 80 in total_carb in a new variable.
dont_eat_this<-data.frame(
fastfood%>%
    filter(total_fat>40 & total_carb>80))

#10.Observations from restaurant Mcdonalds
data%>%
  filter(restaurant== "Mcdonalds")
```
 
 ## Part 2
```{r}
library(skimr)

#11.Display the types of variables in the dataset.
skim(fastfood)

#12.count of observations for each restaurant.
fastfood %>% count(restaurant)

#13.Summarise and display the average number of calories for each restaurant.
fastfood %>%
  group_by(restaurant) %>%
  summarise(calories= mean(calories))

#14.Variable to the dataset, which calculates the average calories per type of restaurant.
average_calories <- data.frame(fastfood %>%
  group_by(restaurant) %>%
  summarise(calories= mean(calories))) # need to replace with mutate

#15.Graph with colour
fastfood %>%
  ggplot(aes(total_fat, restaurant, fill = restaurant)) +
    geom_col()+
  ggtitle("Total fat by restaurant")

```

**Column charts** are useful for showing data changes over a period of time or *for illustrating comparisons among items*. In **column charts**, categories are typically organized along the horizontal axis and values along the vertical axis.

Like bar charts, **column charts** can be used to plot both nominal data and ordinal data, and they can be used instead of a pie chart to plot data with a part-to-whole relationship.
```{r}
#16. A variable to the dataset, which calculates the maximum total fat per type of restaurant.
max_total_fat <- data.frame(fastfood) %>%
  group_by(restaurant) %>%
  summarise(total_fat= max(total_fat))

#17.Observations for Mcdonalds to plot sugar variable against protein
fastfood %>% 
  group_by("Macdonalds")%>%
  ggplot(aes(sugar,protein, colour = restaurant))+
  geom_point()+
  ggtitle("Protein vs Sugar by restaurant")
 
```

## Part 3
```{r}
#18.Variable(s) which should be factors
fastfood$restaurant <- as_factor(fastfood$restaurant)
fastfood$item <- as_factor(fastfood$item)

str(fastfood)
```

```{r}
#19.Create new variable (1/2).
calories_type <- 
  fastfood %>% 
  mutate(calories=cut_number(calories,3, labels=c('low', 'med', 'high')))%>% 
  arrange(calories_type,desc())

#20.Dataviz that shows the distribution of `calories_type` in food items for each type of restaurant. 
calories_type%>% 
  group_by(restaurant) %>% 
  ggplot(aes(restaurant, calories,fill = calories))+
  geom_col()+
  coord_flip()+ 
  theme_minimal()+
  ggtitle("Restaurant calories types")

ggplot(calories_type, aes(total_fat, calories, colour=calories))+
  geom_jitter()+
  coord_flip()+
  facet_wrap(~restaurant)+
  ggtitle("Restaurant calories by total fat")

```

```{r}
as_tibble(fastfood)

#21.Second variable created.
trans_fat_percent <- 
  fastfood %>% 
  mutate(rate=trans_fat/total_fat*100)

#22.Dataviz that shows the distribution of `trans_fat` in food items for each type of restaurant
trans_fat_percent%>% 
  group_by(restaurant) %>% 
  ggplot(aes(rate, trans_fat))+
  geom_jitter()+
  geom_smooth()+
  theme_minimal()
  

ggplot(trans_fat_percent, aes(rate, trans_fat, colour = calories))+
  geom_point()+
  facet_wrap(~restaurant)+
  ggtitle("Trans fat percentage by restaurant")

```
```{r}
#23.Calculate and show the average (mean)  `total_fat` for each type of restaurant
fastfood %>%
  group_by(restaurant) %>%
  summarise(average_total_fat= mean(total_fat))

#24.Dataviz that allow to compare different restaurants on this variable.
fastfood %>%
  group_by(restaurant) %>%
  ggplot(aes(mean(total_fat), restaurant, fill = restaurant)) +
    geom_col()+
  ggtitle("Average fat by restaurant")
  
```




